Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-05-09 cikm2016/nlp.tex
Added intro para to nlp section.

\vidya{need to add a short intro here}

@@

%<Day>     ::= dd (where $dd \in [01-31]$, depending on month/year);

%<Month> := <MonthWord> | <MonthNumber>;

%<MonthWord> := `January' | `February' | `March' | `April' | `May' | `June' | `July' | `August' | `September' | `October' | `November' | `December';
%
%<MonthNumber> := dd (where $dd \in [01-12]$);
%
%<DayOfWeek> ::= `Monday' | `Tuesday' | `Wednesday' | `Thursday' | `Friday' | `Saturday' | `Sunday';
%
%<Hour> ::= <TwelveHour> | <TwentyFourHour>;
%
%<Quarter> ::= `Quarter' dd (where $dd \in [01 - 04]$);
%
%<TwoYear> ::= dd;
%
%<FourYear> := dddd;
%
%<TwelveHour> ::= dd (where $dd \in [00-12]$);
%
%<TwentyFourHour> ::= dd (where $dd \in [00 -23]$);
%
%<AMPM> := `a.m.' | `p.m.';
%
%<d> ::= `0' | `1' | `2' | `3' | `4' | `5' | `6' | `7' | `8' | `9';

>>>>

The second algorithm is a natural language approach to parsing date and time formats. While regular expressions can be used to match strings to known formats, we chose a grammar approach as a generalization of regular expressions. Such an approach provides for greater expressibility and less rigidity, without the expectation of the input string to exactly match against one or more of the known formats. We describe a particular form of grammar called a context-free grammar approach as well as extensions to the rules of the grammar that are inherent to date and time properties such as grammar variants, constraints, and assigning probabilistic weighting through a supervised learning approach.

@@

<Day>     ::= dd (where $dd \in [01-31]$, depending on month/year);

<Month> := <MonthWord> | <MonthNumber>;

<MonthWord> := `January' | `February' | `March' | `April' | `May' | `June' | `July' | `August' | `September' | `October' | `November' | `December';

<MonthNumber> := dd (where $dd \in [01-12]$);

%<DayOfWeek> ::= `Monday' | `Tuesday' | `Wednesday' | `Thursday' | `Friday' | `Saturday' | `Sunday';

%<Hour> ::= <TwelveHour> | <TwentyFourHour>;

%<Quarter> ::= `Quarter' dd (where $dd \in [01 - 04]$);

%<TwoYear> ::= dd;

%<FourYear> := dddd;

%<TwelveHour> ::= dd (where $dd \in [00-12]$);

%<TwentyFourHour> ::= dd (where $dd \in [00 -23]$);

%<AMPM> := `a.m.' | `p.m.';

%<d> ::= `0' | `1' | `2' | `3' | `4' | `5' | `6' | `7' | `8' | `9';
